---
title: "garnett"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Sorted PBMC

```{r}
# devtools::install_github("cole-trapnell-lab/garnett")
library(monocle)
library(garnett)
library(Seurat)

library(org.Mm.eg.db)
library(org.Hs.eg.db)

load("../sorted_pbmc_seuratObj.RData")

celltype <- gsub("(.*)_(.*)", "\\1", names(bcdata$orig.ident))
# create a new CDS object


pbmc_cds <- new("CellDataSet", exprs = as.matrix(GetAssayData(bcdata, "counts")))

# generate size factors for normalization later
pbmc_cds <- estimateSizeFactors(pbmc_cds)



pbmc_classifier <- train_cell_classifier(cds = pbmc_cds,
                                         marker_file = "hsPBMC_markers.txt",
                                         db= org.Hs.eg.db,
                                         cds_gene_id_type = "SYMBOL",
                                         num_unknown = 50,
                                         marker_file_gene_id_type = "SYMBOL")




feature_genes <- get_feature_genes(pbmc_classifier,
                                   node = "root",
                                   db = org.Hs.eg.db)
head(feature_genes)


pbmc_cds <- classify_cells(pbmc_cds, pbmc_classifier,
                           db = org.Hs.eg.db,
                           cluster_extend = TRUE,
                           cds_gene_id_type = "SYMBOL")


head(pData(pbmc_cds))
table(pData(pbmc_cds)$cell_type, celltype)

#save(pbmc_cds, file="garnett_pbmc_sorted.RData")
```

```{r}
load("garnett_pbmc_sorted.RData")

library(scmap)

plot(
  getSankey(
    celltype,
    pData(pbmc_cds)$cell_type,
    
    #plot_height = 400
  )
)

```


# TM Lung 10X - mouse
Note marker file are hs genes

```{r}
# prepare counts
dir_names <- grep("Lung", list.dirs("../tabula_muris/droplet"), value = TRUE)
seuratObjs <- list()

for(j in seq_along(dir_names)){

  projName <- gsub("(.*)/(.*)/(.*)","\\3", dir_names[j])
  projName <- gsub("Lung-","", projName)
  seuratObjs[[projName]] <- CreateSeuratObject(counts = Read10X(dir_names[j]))

}


bcdata <- merge(seuratObjs[[1]],
                  y = Reduce(c,seuratObjs[-1]),
                  add.cell.ids = names(seuratObjs),
                  project = "lung-10x")

bcdata



# prepare labels
meta <- read.csv("../tabula_muris/annotations_droplet.csv") 
meta <- meta[meta$tissue == "Lung",]

meta$cell_id <- paste0(meta$cell,"-1")

table(meta$cell_ontology_class)

table(is.na(match(meta$cell_id, colnames(bcdata))))
bcdata <- bcdata[,match(meta$cell_id, colnames(bcdata))]


celltypes <- meta$cell_ontology_class
names(celltypes) <- meta$cell_id
```


```{r}
lung_cds <- new("CellDataSet", exprs = as.matrix(GetAssayData(bcdata, "counts")))

# generate size factors for normalization later
lung_cds <- estimateSizeFactors(lung_cds)



lung_classifier <- train_cell_classifier(cds = lung_cds,
                                         marker_file = "mmLung_markers.txt",
                                         db= org.Mm.eg.db,
                                         cds_gene_id_type = "SYMBOL",
                                         num_unknown = 50,
                                         marker_file_gene_id_type = "SYMBOL")






feature_genes <- get_feature_genes(lung_classifier,
                                   node = "root",
                                   db = org.Mm.eg.db)
head(feature_genes)


lung_cds <- classify_cells(lung_cds, lung_classifier,
                           db = org.Mm.eg.db,
                           cluster_extend = TRUE,
                           cds_gene_id_type = "SYMBOL")


head(pData(lung_cds))
table(pData(lung_cds)$cell_type, celltypes)


#save(lung_cds, file="garnett_TM_lung_10X.RData")
```


# Dentate Gyrus

```{r}

# query -----
countdata <- read.delim("../cortext_linnarssonlab/GSE95315_10X_expression_data_v2.tab") # appropriate as query
table(as.character(countdata[2,]))
query_labels <- as.character(countdata[2,])[-1]
rownames(countdata) <- countdata$cellid
countdata <- countdata[-c(1:2),]

countdata$cellid <- NULL

brain_cds <- new("CellDataSet", exprs = data.matrix(countdata))

# generate size factors for normalization later
brain_cds <- estimateSizeFactors(brain_cds)



brain_classifier <- train_cell_classifier(cds = brain_cds,
                                         marker_file = "mmBrain_markers.txt",
                                         db= org.Mm.eg.db,
                                         cds_gene_id_type = "SYMBOL",
                                         num_unknown = 50,
                                         marker_file_gene_id_type = "SYMBOL")






feature_genes <- get_feature_genes(brain_classifier,
                                   node = "root",
                                   db = org.Mm.eg.db)
head(feature_genes)


brain_cds <- classify_cells(brain_cds, brain_classifier,
                           db = org.Mm.eg.db,
                           cluster_extend = TRUE,
                           cds_gene_id_type = "SYMBOL")


head(pData(brain_cds))
table(pData(brain_cds)$cell_type, celltypes)

plot(
  getSankey(
    query_labels,
    pData(brain_cds)$cell_type,
    
    #plot_height = 400
  )
)


#save(brain_cds, file="brain_preds_garnett.RData")

