---
title: "scDECAF_label_mapping"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    code_folding: hide
    fig_width: 10
    fig_height: 10
---



```{r, echo=FALSE}

### --- SETUP
library(scRNAseq)
library(ggplot2)
library(scran)
library(scater)
library(networkD3)
library(dplyr)
library(RColorBrewer)

seger <- SegerstolpePancreasData()
baron <- BaronPancreasData('human')
setwd("/stornext/Home/data/allstaff/w/whitfield.h/scDECAF/")
panglao <- read.delim("./label_mapping/PanglaoDB_markers_27_Mar_2020.tsv")
cellmarker <- read.delim("./label_mapping/all_cell_markers.txt")

MalvikaResults <- read.csv("./label_mapping/ggdat_pancreas.csv", sep=",", skip=7)
MalvikaResults_lung <- read.csv("./label_mapping/ggdat_lung.csv", sep=",", skip=7)


### --- Process markers
immune_cells_panlog <- panglao[panglao$organ %in% "Pancreas", c("cell.type", "official.gene.symbol")]
immune_cells_panlog <- unique(immune_cells_panlog)
immune_cells_panlog <- split(immune_cells_panlog$official.gene.symbol, as.factor(immune_cells_panlog$cell.type))
pancreas_markers <- cellmarker[cellmarker$tissueType %in% c("Pancreas","Pancreatic acinar tissue","Pancreatic islet"),]
#table(pb_markers$cellName)
pancreas_markers <- unique(pancreas_markers)
pancreas_markers <- split(pancreas_markers$geneSymbol, as.factor(pancreas_markers$cellName))
# either replace Beta cell signature or drop highly expressed CD99 from endo signature shared with beta signature
keep_pancreas <- c("Endocrine progenitor cell")
pancreas_markers <- pancreas_markers[keep_pancreas]
pancreas_markers <- lapply(pancreas_markers, FUN=function(x) {
  z <- unlist(strsplit(x, split = ","))
  z <- unique(gsub(" |\\[|\\]","", z))
})
pancreas_markers[[1]] <- c(pancreas_markers[[1]], c("DISP2", 
                                                    #"CD99" ,
                                                    "LRP11",
                                                    "SEZ6L2"
                                                    #"SLC30A8"
                                                    ))
immune_cells_panlog <- c(immune_cells_panlog, pancreas_markers)
immune_cells_panlog <- immune_cells_panlog[grep("Pancreatic progenitor cells", names(immune_cells_panlog), invert = TRUE)]

pancreas_sigs <- immune_cells_panlog


######## ------------------ SANKEY ----------------- #################

MakeSankey_only2 <- function(ListOfLabels_1, ListOfLabels_2){
  
  Sankey_df <- data.frame(Labels_1=ListOfLabels_1,
                          Labels_2=ListOfLabels_2) 
  
  Weighted_table <- table(Sankey_df[, c("Labels_1", "Labels_2")])
  
  source_vector <- c()
  target_vector <- c()
  count_vector <- c()
  
  for (i in rownames(Weighted_table)){
    for (j in colnames(Weighted_table)){
      iWeight <- Weighted_table[i, j]
      if (iWeight != 0){
        source_vector <- append(source_vector, i)
        target_vector <- append(target_vector, j)
        count_vector <- append(count_vector, iWeight)
      }
    }
  }
  
  SankeyLinks_df <- data.frame(Source=source_vector,
                               Target=target_vector,
                               Count=count_vector)
  nodes <- data.frame(name=c(as.character(SankeyLinks_df$Source), as.character(SankeyLinks_df$Target)) %>% unique())
  
  # With networkD3, connection must be provided using id, not using real name like in the links dataframe.. So we need to reformat it.
  SankeyLinks_df$IDsource <- match(SankeyLinks_df$Source, nodes$name)-1 
  SankeyLinks_df$IDtarget <- match(SankeyLinks_df$Target, nodes$name)-1
  
  
  sankeyNetwork(Links = SankeyLinks_df, Nodes = nodes,
                Source = "IDsource", Target = "IDtarget",
                Value = "Count", NodeID = "name", 
                sinksRight=FALSE, fontSize=14, fontFamily="Helvetica")
  
  
  # save the widget
  # library(htmlwidgets)
  # saveWidget(p, file=paste0( getwd(), "/HtmlWidget/sankeyBasic1.html"))
  
}

MakeSankey_3 <- function(ListOfLabels_1, ListOfLabels_2, ListOfLabels_3){
  
  NewList_3 <- c()
  for (i in ListOfLabels_3){
    if (i == "NK cells"){
      NewList_3 <- append(NewList_3, "NK cells (fine)")
    }
    else{ NewList_3 <- append(NewList_3, i)}
  }
  
  library(networkD3)
  library(dplyr)
  
  Sankey_df <- data.frame(Labels_1=ListOfLabels_1,
                          Labels_2=ListOfLabels_2, Labels_3=NewList_3) 
  
  Weighted_table_1to2 <- table(Sankey_df[, c("Labels_1", "Labels_2")])
  Weighted_table_2to3 <- table(Sankey_df[, c("Labels_2", "Labels_3")])
  
  source_vector <- c()
  target_vector <- c()
  count_vector <- c()
  
  for (i in rownames(Weighted_table_1to2)){
    for (j in colnames(Weighted_table_1to2)){
      iWeight <- Weighted_table_1to2[i, j]
      if (iWeight != 0){
        source_vector <- append(source_vector, i)
        target_vector <- append(target_vector, j)
        count_vector <- append(count_vector, iWeight)
      }
    }
  }
  
  for (i in rownames(Weighted_table_2to3)){
    for (j in colnames(Weighted_table_2to3)){
      iWeight <- Weighted_table_2to3[i, j]
      if (iWeight != 0){
        source_vector <- append(source_vector, i)
        target_vector <- append(target_vector, j)
        count_vector <- append(count_vector, iWeight)
      }
    }
  }
  
  SankeyLinks_df <- data.frame(Source=source_vector,
                               Target=target_vector,
                               Count=count_vector)
  nodes <- data.frame(name=c(as.character(SankeyLinks_df$Source), as.character(SankeyLinks_df$Target)) %>% unique())
  
  # With networkD3, connection must be provided using id, not using real name like in the links dataframe.. So we need to reformat it.
  SankeyLinks_df$IDsource <- match(SankeyLinks_df$Source, nodes$name)-1 
  SankeyLinks_df$IDtarget <- match(SankeyLinks_df$Target, nodes$name)-1
  
  sankeyNetwork(Links = SankeyLinks_df, Nodes = nodes,
                Source = "IDsource", Target = "IDtarget",
                Value = "Count", NodeID = "name", 
                sinksRight=FALSE, fontSize=14, fontFamily="Helvetica")
  
  
  # save the widget
  # library(htmlwidgets)
  # saveWidget(p, file=paste0( getwd(), "/HtmlWidget/sankeyBasic1.html"))
  
}

MakeSankey_only2(replace(MalvikaResults_lung$scDECAF, MalvikaResults_lung$scDECAF=="", "NA"),
                 replace(MalvikaResults_lung$true_labels, MalvikaResults_lung$true_labels=="", "NA"))

```

```{rm echo=FALSE, eval=FALSE}
### --- Process baron
set.seed(1000)
clusters <- quickCluster(baron)
baron <- scran::computeSumFactors(baron, cluster=clusters, min.mean=0.1)
baron <- logNormCounts(baron)
baron <- runUMAP(baron)
baron <- runPCA(baron)
baron <- runUMAP(baron,name = "PCA_UMAP", dimred ="PCA")
plotReducedDim(baron, colour_by="label", dimred="PCA")
```


# Pancreas Labels 

\vspace{12pt}

The pancreatic islet cell types include: 
* alpha cells, which produce glucagon
* beta cells, which produce insulin
* delta cells, which produce somatostatin
* Epsilon produce ghrelin
* PP cells, which produce pancreatic polypeptide.
* Exocrine pancreas is made up of acinar and duct cells, which are endothelial-like but with differing functions
* The pancreatic acinar cell is the functional unit of the exocrine pancreas. It synthesizes, stores, and secretes digestive enzymes. Under normal physiological conditions, digestive enzymes are activated only once they have reached the duodenum.
*  Normally, pancreatic stellate cells (PSCs) are quiescent and regulate extracellular matrix (ECM) production.

```{r, echo=FALSE, eval=FALSE}
# https://www.researchgate.net/profile/Xiang-Gao-80/publication/301696654/figure/tbl1/AS:667934447919124@1536259390741/Cell-types-in-pancreatic-islets.png

# Acinar -- https://www.123rf.com/photo_97575048_stock-vector-acinar-cell-of-the-pancreas-acinus-infographics-vector-illustration-on-isolated-background-.html

# Acinar vs alpha/beta/delta -- https://d45jl3w9libvn.cloudfront.net/jaypee/static/books/9789351528531/Chapters/images/2-1.jpg

# https://www.researchgate.net/publication/318578913/figure/fig4/AS:675876006031361@1538152805614/New-heterogeneities-in-pancreatic-cell-types-Table-summarizing-the-new-concepts-and.jpg

# https://mmegias.webs.uvigo.es/02-english/a-iconos/epitelio-tipos-glandulas.png
# http://anatomyandphysiologyi.com/wp-content/uploads/2013/06/glandular-epithelia.jpg
```

\vspace{12pt}

## Cell Types {.tabset}

\vspace{12pt}

### Signatures


```{r}
sig_lengths <- lapply(pancreas_sigs, function(x){length(x)})
dat_x <- data.frame(sigs = names(sig_lengths), len = as.vector(unlist(sig_lengths)))
ggplot(data=dat_x, aes(x=sigs, y=len))+geom_col()+coord_flip()
```


### Seger


```{r}
dat_x <- data.frame(labels = names(table(seger$`cell type`)), numbCells = as.vector(table(seger$`cell type`)))
ggplot(data=dat_x, aes(x=labels, y=numbCells))+geom_col()+coord_flip()
```


### Baron


```{r}

dat_x <- data.frame(labels = names(table(baron$label)), numbCells = as.vector(table(baron$label)))
ggplot(data=dat_x, aes(x=labels, y=numbCells))+geom_col()+coord_flip()
```
\vspace{12pt}

## Mapping


\vspace{12pt}

```{r, echo=FALSE}
### --- Export mappings

baron_labels <- unique(baron$label)
seger_labels <- c("acinar cell", "beta cell", "delta cell", 
                  "PSC cell", "ductal cell", "alpha cell",
                  "epsilon cell", "gamma cell", "endothelial cell",
                  "PSC cell", "MHC class II cell", "",
                  "mast cell", "")
panglao_labels <- c("Acinar cells", "Beta cells", "Delta cells", 
                  "Pancreatic stellate cells", "Ductal cells", "Alpha cells",
                  "Epsilon cells", "Gamma (PP) cells", "Endothelial cells",
                  "Pancreatic stellate cells", "Macrophages", "Peri-islet Schwann cells",
                  "Mast cells", "T cytotoxic cells")
label_mapping = data.frame(baron=baron_labels, seger=seger_labels, panglao=panglao_labels)
write.csv(label_mapping, file="./label_mapping/label_mapping.csv", row.names=FALSE)
```


# Lung Labels


```{r, echo=FALSE}


### --- LOAD LUNG PREDS
load("./label_mapping/TM_lung_10x_scDECAD_preds.RData")
ann_res$true_label <- as.vector(celltype_dict[gsub("-1","", ann_res$cell)])

load("./label_mapping/SingleR_preds_TM_lung_10X.RData")
predicted_labels <- pred.tmLungs$labels
true_labels <- lung_meta_dataset$cell_ontology_class
lung_predictions <- data.frame(label =true_labels , pred=predicted_labels)
#table(lung_predictions[lung_predictions$label=="myeloid cell",]$pred)

lung_predictions$label <- replace(lung_predictions$label, lung_predictions$label=="","None")
lung_predictions_scDECAF <- data.frame(label =ann_res$true_label,
                                       pred=ann_res$pred_celltype)


PlotSank <- function(dat, label_to_check){
  temp <- dat[dat$label == label_to_check,]
  MakeSankey_only2(temp$label, temp$pred)
}

PlotSank_pred <- function(dat, label_to_check){
  temp <- dat[dat$pred == label_to_check,]
  MakeSankey_only2(temp$label, temp$pred)
}

singleR_pred_dict <- pred.tmLungs$labels
names(singleR_pred_dict) <- rownames(pred.tmLungs)

scDECAF_pred_dict <- ann_res$pred_celltype
names(scDECAF_pred_dict) <- rownames(ann_res)
  

### --- LOAD LUNG METADATA
lung_meta <- read.csv("./label_mapping/mouse_droplet_TMS_metadata.csv")
lung_meta_dataset <- read.csv("./label_mapping/annotations_droplet.csv") # tabular muris
lung_meta_dataset <- lung_meta_dataset[lung_meta_dataset$tissue == "Lung",]

celltype_dict <- lung_meta_dataset$cell_ontology_class
names(celltype_dict) <- lung_meta_dataset$cell
  
### --- LOAD LUNG DATA (TM)
#load("./label_mapping/TM_lung_10X_seuratObj.RData")
#DefaultAssay(object = bcdata) <- "RNA"
#TM_lung_sce <- as.SingleCellExperiment(bcdata, assay="RNA")
#TM_lung_sce <- TM_lung_sce[rowSums(counts(TM_lung_sce)>0)>0,]
#set.seed(1000)
#clusters <- quickCluster(TM_lung_sce)
#TM_lung_sce <- scran::computeSumFactors(TM_lung_sce, cluster=clusters, min.mean=0.1)
#TM_lung_sce <- logNormCounts(TM_lung_sce)
#TM_lung_sce <- runUMAP(TM_lung_sce)
#TM_lung_sce <- runTSNE(TM_lung_sce)
#TM_lung_sce$celltype <- as.vector(celltype_dict[gsub("-1","", colnames(TM_lung_sce))])
#TM_lung_sce$SingleR_pred <- as.vector(singleR_pred_dict[colnames(TM_lung_sce)])
#TM_lung_sce$scDECAF_pred <- as.vector(scDECAF_pred_dict[colnames(TM_lung_sce)])
#save(TM_lung_sce, file="./label_mapping/TM_lung_sce.RData")

load(file="./label_mapping/TM_lung_sce.RData")

png("./label_mapping/TabularMuris_UMAP_ByCelltype.png",width = 600, height = 600)
plotReducedDim(TM_lung_sce, dimred = "UMAP", colour_by = "celltype")
dev.off()

TargetTSNE <- function(sce_obj, column, labels, alpha=0.7, size=1, pal="Set3"){
  labels_to_colour <- unique(sce_obj[[column]][sce_obj[[column]] %in% labels])
  
  col_pal <- brewer.pal(length(labels_to_colour), pal)
  names(col_pal) <- labels_to_colour
  
  for (i in unique(setdiff(sce_obj[[column]], labels))){
    col_pal[[i]] <- "#808080"
  }
  
  rl=1
  tsne <- plotReducedDim(sce_obj, dimred = "TSNE", colour_by = column, point_alpha=alpha, point_size=size)+
    scale_colour_manual(values=col_pal, limits=unique(labels_to_colour))+
    theme(legend.text = element_text(size = rel(rl)*1),
          legend.title = element_text(size = rel(rl)*1.1, face = 'bold'),
          legend.position = 'right',panel.border = element_rect(colour = NA),# legend.text.align=0.5,
          panel.grid.minor = element_blank(),
          panel.grid.major = element_blank(),
          axis.text.y = element_blank(), axis.text.x = element_blank(), 
          axis.line.y = element_blank(),axis.line.x = element_blank(),
          axis.ticks.y=element_blank(), axis.ticks.x=element_blank(),
          axis.title.y =element_blank(),  axis.title.x=element_blank(),legend.box.margin=margin(0,0,0,0),
          legend.spacing = unit(0, 'cm'))+ labs(color = "Cell Type")+
    guides(color=guide_legend(nrow=length(unique(labels_to_colour)),byrow=TRUE, override.aes = list(size=4)))
  
  return(tsne)
}

tsne_1 <- plotReducedDim(TM_lung_sce, dimred="TSNE", colour_by="celltype")
tsne_2 <- TargetTSNE(TM_lung_sce, "SingleR_pred", 
                     lung_predictions[lung_predictions$label == "classical monocyte",]$pred, 
                      alpha=0.7, size=1.1, pal="Dark2")

tsne_2 <- TargetTSNE(TM_lung_sce, "scDECAF_pred", 
                     lung_predictions_scDECAF[lung_predictions_scDECAF$label == "non-classical monocyte",]$pred, 
                        alpha=0.7, size=1.1, pal="Set3")

grid.arrange(tsne_1, tsne_2, nrow = 1)

tSNE_loci <- reducedDim(TM_lung_sce, "TSNE")
```

\vspace{12pt}

## Cell Types {.tabset}

\vspace{12pt}


### Lung Atlas (TMS) - reference


```{r}

dat_x <- data.frame(labels = names(table(lung_meta$free_annotation)), numbCells = as.vector(table(lung_meta$free_annotation)))
ggplot(data=dat_x, aes(x=labels, y=numbCells))+geom_col()+coord_flip()
```

## Tabular Muris -- Dataset


```{r}

dat_x <- data.frame(labels = names(table(lung_meta_dataset$cell_ontology_class)), numbCells = as.vector(table(lung_meta_dataset$cell_ontology_class)))
ggplot(data=dat_x, aes(x=labels, y=numbCells))+geom_col()+coord_flip()
```


\vspace{12pt}

## Mapping


\vspace{12pt}

```{r, echo=FALSE}

## To find out:
# - What do they define as Myeloid? Anything that isn't one of the listed myeloid?
# - classical vs non-classical monocyte?

### Lung atlas to tabular muris
lung_label_dict <- c()

lung_label_dict["Myeloid Dendritic Type 1"] = "myeloid cell"
lung_label_dict["Myeloid Dendritic Type 2"] = "myeloid cell"
lung_label_dict["Interstitial Macrophage"] = "myeloid cell"
lung_label_dict["Nonclassical Monocyte"] = "myeloid cell"
lung_label_dict["Plasmacytoid Dendritic"] = "myeloid cell"
lung_label_dict["Proliferating Dendritic"] = "myeloid cell"

lung_label_dict["Classical Monocyte"] = "classical monocyte"
lung_label_dict["Intermediate Monocyte"] = "classical monocyte"
lung_label_dict["Nonclassical Monocyte"] = "non-classical monocyte"
lung_label_dict["Intermediate Monocyte"] = "non-classical monocyte"

# not otherwise labelled white blood cells -- i.e. excluding lymphocytes (T/B/NK)
lung_label_dict["Neutrophil"] = "leukocyte"
lung_label_dict["Basophil"] = "leukocyte"
lung_label_dict["Nonclassical Monocyte"] = "leukocyte"
# + Eosinophil

lung_label_dict["Basophil"] = "mast cell"
lung_label_dict["Natural Killer"] =  "natural killer cell"
lung_label_dict["Proliferating NK"] =  "natural killer cell"
lung_label_dict["Natural Killer T"] =  "natural killer cell"
lung_label_dict["CD4+ T"] = "T cell"
lung_label_dict["CD8+ T"] = "T cell"
lung_label_dict["Natural Killer T"] = "T cell"
lung_label_dict["Proliferating T"] = "T cell"
lung_label_dict["Regulatory T"] = "T cell"
lung_label_dict["Plasma"] = "B cell"
lung_label_dict["B"] = "B cell"
lung_label_dict["Zbtb32+ B"] = "B cell"

lung_label_dict["Alveolar Macrophage"] = "alveolar macrophage"
lung_label_dict["Proliferating Alveolar Macrophage"] = "alveolar macrophage"

lung_label_dict["Ciliated"] = "ciliated columnar cell of tracheobronchial tree"
lung_label_dict["Adventitial Fibroblast"] = "stromal cell"
lung_label_dict["Airway Smooth Muscle"] = "stromal cell"
lung_label_dict["Alveolar Fibroblast"] = "stromal cell"
lung_label_dict["Myofibroblast"] = "stromal cell"

lung_label_dict["Pulmonary alveolar type II cells"] = "type II pneumocyte"
lung_label_dict["Epithelial cell"] = "type II pneumocyte"

lung_label_dict["Capillary"] = "lung endothelial cell"
lung_label_dict["Vein"] = "lung endothelial cell"
lung_label_dict["Capillary Aerocyte"] = "lung endothelial cell"
lung_label_dict["Artery"] = "lung endothelial cell"
lung_label_dict["Lympatic"] = "lung endothelial cell"


### Panglao to tabular muris
lung_label_panglao_dict <- c()
lung_label_panglao_dict["Monocytes"] = "classical monocyte"
lung_label_panglao_dict["Monocytes"] = "non-classical monocyte"

lung_label_panglao_dict["Macrophages"] = "myeloid cell"
lung_label_panglao_dict["Monocytes"] = "myeloid cell"
lung_label_panglao_dict["Dendritic cells"] = "myeloid cell"

lung_label_panglao_dict["Basophil"] = "mast cell"
lung_label_panglao_dict["Mast cells"] = "mast cell"

lung_label_panglao_dict["Neutrophil"] = "leukocyte"
lung_label_panglao_dict["Basophil"] = "leukocyte"
lung_label_panglao_dict["Eosinophil"] = "leukocyte"
lung_label_panglao_dict["Monocytes"] = "leukocyte"

lung_label_panglao_dict["B cells"] = "B cell"
lung_label_panglao_dict["T cells"] = "T cell"
lung_label_panglao_dict["Natural killer T cells"] = "T cell"
lung_label_panglao_dict["Natural killer T cells"] = "natural killer cell"
lung_label_panglao_dict["NK cells"] = "natural killer cell"

## -- From lung
lung_label_panglao_dict["Alveolar macrophages"] = "alveolar macrophage"
lung_label_panglao_dict["Pulmonary alveolar type II cells"] = "type II pneumocyte"
lung_label_panglao_dict["Ciliated cells"] = "ciliated columnar cell of tracheobronchial tree"

## -- From vasculature
lung_label_panglao_dict["Endothelial cells"] = "lung endothelial cell"

## -- From Connective tissue
lung_label_panglao_dict["Fibroblasts"] = "stromal cell"
lung_label_panglao_dict["Stromal cells"] = "stromal cell"

## -- From Smooth muscle
lung_label_panglao_dict["Airway smooth muscle cells"] = "stromal cell"
lung_label_panglao_dict["Myofibroblasts"] = "stromal cell"


### -->> Make panglao dataset for them...
#6 epithelial (basal, club, multiciliated,neuroendocrine, alveolar type 1, and alveolar type 2 cells)


##### ----- OLD

tabular_muris_labels <- c("myeloid cell","myeloid cell","myeloid cell", 
                          
                          "alveolar macrophage", 
                          "B cell",  "B cell", 
                          "natural killer cell", "natural killer cell", "natural killer cell",
                          "T cell", "T cell", "T cell", "T cell", "T cell", 
                          "lung endothelial cell",  "lung endothelial cell",  "lung endothelial cell",  "lung endothelial cell",  "lung endothelial cell", 
                          "stromal cell","stromal cell","stromal cell","stromal cell","stromal cell",
                          "non-classical monocyte",
                          "leukocyte","leukocyte","leukocyte", 
                          "classical monocyte",
                          "ciliated columnar cell of tracheobronchial tree", 
                          "type II pneumocyte", 
                          "mast cell")

LungAtlas_labels <- c("myeloid cell","myeloid cell","myeloid cell", 
                          "alveolar macrophage", 
                          "B cell",  "B cell", 
                          "natural killer cell", "natural killer cell", "natural killer cell",
                          "T cell", "T cell", "T cell", "T cell", "T cell", 
                          "lung endothelial cell",  "lung endothelial cell",  "lung endothelial cell",  "lung endothelial cell",  "lung endothelial cell", 
                          "stromal cell","stromal cell","stromal cell","stromal cell","stromal cell",
                          "non-classical monocyte",
                          "leukocyte","leukocyte","leukocyte", 
                          "classical monocyte",
                          "ciliated columnar cell of tracheobronchial tree", 
                          "type II pneumocyte", 
                          "mast cell")

TMS_ref_labels <- c("Adventitial Fibroblast","Airway Smooth Muscle", 
                    "Alox5+ Lymphocytes",                
                    "Alveolar Epithelial Type 2", "Alveolar Fibroblast",
                    "Alveolar Macrophage","Artery",
                    "B", "Basophil",
                    "Capillary","Capillary Aerocyte",
                    "Ccr7+ Dendritic","CD4+ T","CD8+ T",
                    "Ciliated",
                    "Classical Monocyte",
                    "Club",
                    "Intermediate Monocyte",
                    "Interstitial Macrophage","Ly6g5b+ T","Lympatic",
                    "Myeloid Dendritic Type 1",        
         "Myeloid Dendritic Type 2",
         "Myofibroblast",
         "Natural Killer","Natural Killer T", 
         "Neuroendocrine",
         "Neutrophil","Nonclassical Monocyte","Pericyte","Plasma","Plasmacytoid Dendritic",
         "Proliferating Alveolar Macrophage",
         "Proliferating Classical Monocyte","Proliferating Dendritic", 
         "Proliferating NK","Proliferating T",
         "Regulatory T", "Vein","Zbtb32+ B"   
                    )

panglao_lung_labels <- c("Dendritic cells","Myeloid-derived suppressor cells","", 
                          "Alveolar macrophages", 
                          "B cells",  "B cells", 
                          "NK cells", "NK cells", "NK cells",
                          "T cells", "T cells", "T cells", "T cells", "T cells", 
                          "lung endothelial cell",  "lung endothelial cell",  "lung endothelial cell",  "lung endothelial cell",  "lung endothelial cell", 
                          "stromal cell","stromal cell","stromal cell","stromal cell","stromal cell",
                          "Monocytes",
                          "Basophils","Neutrophils", "Eosinophils",
                          "Monocytes",
                          "Ciliated cells", 
                          "Pulmonary alveolar type II cells", 
                          "Mast cells")

panglao_organ <-  c( "Immune system","Immune system","Immune system",
                "Lungs", 
                "Immune system",  "Immune system", 
              "Immune system","Immune system","Immune system",
            "Immune system", "Immune system","Immune system", "Immune system","Immune system",   
                          "lung endothelial cell",  "lung endothelial cell",  "lung endothelial cell",  "lung endothelial cell",  "lung endothelial cell", 
                          "stromal cell","stromal cell","stromal cell","stromal cell","stromal cell",
                           "Immune system", 
                           "Immune system",  "Immune system", "Immune system", 
                          "Immune system", 
                          "Lungs", 
                          "Lungs", 
                          "Immune system")

lung_mapping <- data.frame(TabulaMuris=tabular_muris_labels,LungAtlas=TMS_ref_labels, panglao=panglao_lung_labels,panglao_organs=panglao_organ)

### I would recommend removing mast cells...
write.csv(lung_mapping, file="./label_mapping/label_mapping_lung.csv", row.names=FALSE)

# Alox5+ Lymphocytes NOT T cell
# Plasma NOT B cell
## DCs: https://media.biocompare.com/m/37/article/572982-dendritic-cell-figure-2.jpg
# Plasmacytoid Dendritic is lymphoid
# Endothelial vs stromal -- https://www.ahajournals.org/doi/10.1161/CIRCULATIONAHA.120.052318
# Intermediate Monocytes are a rare population and it is unknown which of classical or non classical monocytes they resemble more
```

